\documentclass[12pt]{article}

\input{format}



\begin{document}
\raggedright
\huge
Astro2020 Science White Paper \linebreak

Opportunities in Time-Domain Extragalactic Astrophysics with the NASA Near-Earth Object Camera (NEOCam) \linebreak
\normalsize

\noindent \textbf{Thematic Areas:} 
\hspace*{60pt} $\square$ Planetary Systems 
\hspace*{10pt} $\square$ Star and Planet Formation 
\hspace*{20pt} 
\linebreak
$\square$ Formation and Evolution of Compact Objects 
\hspace*{31pt} $\square$ Cosmology and Fundamental Physics 
\linebreak
  $\square$  Stars and Stellar Evolution \hspace*{1pt} 
 $\square$ Resolved Stellar Populations and their Environments \hspace*{40pt} 
\linebreak
  $\square$    Galaxy Evolution   \hspace*{45pt} $\square$             
Multi-Messenger Astronomy and Astrophysics \hspace*{65pt} \linebreak
  
\textbf{Principal Author:}

Name: Nicholas P. Ross	
 \linebreak						
Institution:  University of Edinburgh
 \linebreak
Email: npross@roe.ac.uk
 \linebreak
Phone:  +44 (0)131-668 8351
 \linebreak
 
\textbf{Co-authors:} (names and institutions)
  \linebreak
YOUR NAME HERE!!!!!

\textbf{Abstract  (optional):}


\pagebreak
%%Insert your white paper text here (max of five pages including figures). 

\begin{quotation}
\noindent
{\it 
This White Paper motivates the {\it Time Domain Extragalactic Science case} for 
the NASA Near-Earth Object Camera (NEOCam). 
%%
%%
%%
NEOCam\footnote{\href{https://neocam.ipac.caltech.edu/}{https://neocam.ipac.caltech.edu/}} is a NASA Planetary mission, currently in Phase A, whose goal is to discover and characterize asteroids and comets, to assess the hazard to Earth from near-Earth objects, and to study the origin, evolution, and fate of asteroids and comets.
%% 
However, NEOCam will cover 68\% of the 'extragalactic sky' ($|b| > 30$ deg), 
%%
and as NEOWISE-R has recently proved, infrared light curve information is now vital for characterising the $\gtrsim$10 million AGN candidates identified from their IR emission. 
%%
As such, for relatively very little additional cost, adding the capacity for additional data processing (and/or alerting) would have a massive scientific and legacy impact on extragalactic time domain science. 
}
\noindent
\end{quotation}


\smallskip
\smallskip
\noindent
%{\bfseries \large \textsc{\textcolor{Cerulean}{Continuing the NASA IR Space Telescope Legacy}}}
{\bfseries \textsc{\textcolor{Cerulean}{Time Domain Extragalactic Science Now and into the Net Decade}}}

\smallskip
\noindent
Having started in the 2010s with Pan-STARRS, PTF and ZTF, with the arrival of LSST, time domain extragalactic science will be a mature field in the 2020s. However, only with the advent of the Wide-field Infrared Survey Explorer (WISE) and Near-Earth Object Wide-field Infrared Survey Explorer Reactivation missions (NEOWISE-R) has the field of extragalactic science had its first scientifically interesting time-domain mid-infrared dataset (NPR:: I {\it think} this is true??!!)


\smallskip
\smallskip
\noindent
%{\bfseries \large \textsc{\textcolor{Cerulean}{Continuing the NASA IR Space Telescope Legacy}}}
{\bfseries \textsc{\textcolor{Cerulean}{Continuing the NASA IR Space Telescope Legacy}}} 

\smallskip
\noindent
As the Infrared Astronomical Satellite (IRAS; 1983 January 25th launch), 
%the Infrared Space Observatory (ISO, cite) in the mid-1990s, 
the Spitzer Space Telescope (SSC; 2003 August 25th launch) and the Wide-field
Infrared Survey Explorer (WISE; 2009 December 14th launch) satellites all show 
how powerful infrared space telescopes, with moderate-sized primary mirrors are.

\smallskip
\smallskip
\noindent
NEOCam would survey the Solar System at two simultaneous thermal IR bandpasses. 
%NEOCam would detect and track the majority of potentially hazardous asteroids during its planned 5-year lifetime, and constrain the population of smaller objects that could pose a threat to Earth. NEOCam 
but would also provide a synoptic survey of two-thirds of the thermal infrared sky at 4 - 5.2$\mu$m and  6 - 10$\mu$m using a large field of view of 11.56 square degrees. 
%We will describe the mission as proposed, and the expected data products.



%\smallskip
%\smallskip
%\noindent
%Nunc semper quam et leo interdum vulputate eu quis magna. Sed nec arcu at orci egestas convallis. Aenean quam velit, aliquam vitae viverra in, elementum vel elit. Nunc suscipit aliquet sapien a suscipit. Cras nulla ipsum, posuere eu fringilla sit amet, dapibus ultricies nulla. Nullam eu augue id purus mollis dignissim sed et libero. Phasellus eget justo sed neque pellentesque egestas nec id arcu. Donec facilisis pulvinar sapien et fringilla. Suspendisse vestibulum rhoncus sapien id laoreet. Morbi et orci vitae tortor imperdiet imperdiet. In hac habitasse platea dictumst. Vivamus vel neque id mi ultrices tristique. Integer quam libero, ornare vel gravida in, feugiat a ante. Nam dapibus, tellus vitae pellentesque cursus, dui nisl egestas augue, non fermentum nisl est nec nisi. Vestibulum nec mi justo, eget dapibus velit.


\smallskip
\smallskip
\noindent
{\bfseries \textsc{\textcolor{Cerulean}{The NASA Near-Earth Object Camera (NEOCam)}}}

\textsl{\textsc{Overview:}}
NEOCam is a NASA Planetary mission, currently in Phase A, whose goal
is to discover and characterize asteroids and comets, to assess the
hazard to Earth from near-Earth objects, and to study the origin,
evolution, and fate of asteroids and comets. NEOCam is a
single-instrument, 50cm diameter telescope that will observe in two
simultaneous channels, called NC1 and NC2, which cover wavelengths of
4.0-5.2 $\mu$m and 6.0-10.0$\mu$m, respectively. There are four Teledyne
2k$\times$2K HgCdTe arrays per channel with 3.00'' pixels in each. The entire
celestial sphere between ecliptic latitudes of +40$^{\circ}$ to -40$^{\circ}$ will
continually be mapped over the course of the 5-yr mission, and over 12
yr for the design lifetime. 
%%
{\it NEOCam will provide a synoptic survey of two-thirds of the thermal infrared sky at 4-5.2 microns and 6-10 microns.}

\smallskip
\smallskip
\noindent
\textsl{\textsc{Cadence:}} Estimates of on-board overheads and resulting orbit quality are still being refined, but the current data cadence is as follows. The observing pattern consists of a four-peat of a six-position dither (a quick sequence of six images with 28s integration time each) with 2h gaps between each repeat. This four-peat will recur $\sim$13.2d later as long as the 75d visibility window is still open. Afterward, there will be a gap of 215d until the next visibility window opens and the pattern begins again. On average in a typical visibility window, there are $\sim$23 of these six-position dither sequences (a little less than 6 four-peats), $\sim$234 over 5yr, and $\sim$562 over 12yr.

\smallskip
\smallskip
\noindent
\textsl{\textsc{Depth:}} Each of the six-position dither sequences is expected to have an S/N=5 sensitivity of 65-120 $\mu$Jy for NC1 and 110-280 $\mu$Jy for NC2, for low to high zodiacal backgrounds. 

\smallskip
\smallskip
\noindent
\textsl{\textsc{Data Products:}} NEOCam processing will create images and lists of characterized sources from each individual exposure and each stacked six-dither position sequence. It will also create differenced images by subtracting a static reference image, and a list of the characterized transient detections also produced. Because the goal of NEOCam is to provide and characterize moving objects within the solar system, coaddd and source extractions over longer timescales are not provided, the one exception being yearly builds to create new static images (without any source detection or characterization) of the sky to use in image differencing. No alerting mechanism is provided for astrophysical transient events.  

\smallskip
\smallskip
\noindent
{\bf To realize the full potential of the NEOCam data for astrophysical research, additional data products and alerting infrastructure are needed, as discussed below. For a relatively small investment, NASA can leverage the existing NEOCam data to cover a wide range of extragalactic, time-domain, research.}


\smallskip
\smallskip
\noindent
In particular, extragalactic science has always benefitted from space-based IR operations, and this will continue in the 2020s with JWST, as well as new very wide-field observatories such as NEOCam. 


Here we highlight 3 particular extragalactic science cases all of which have a time-domain aspect. These are Type Ia SNe; ``Changing Look Quasars'' and IR variable signatures of Gravitational wave events. As such, these range in established techniques via very recent progress to brand new parameter space. 


%\smallskip
%\smallskip
%\noindent
%\textbf{\textsc{The world's largest digital camera, billions of objects and  the first motion picture of our universe: }} 
%
%- IR SNe, Type Ias?

\smallskip
\smallskip
\noindent

\smallskip
\smallskip
\noindent
\textbf{\textsc{Near-infrared Variability: A cornerstone of AGN and Quasar investigations in the next Decade and beyond:}} 

\smallskip
\smallskip
\noindent
%% From:: 
%%   The Central Engine of Active Galactic Nuclei
%%   ASP Conference Series, Vol. 373, Xi’an, China, 16–21 October, 2006 eds. L. C. Ho and J.-M. Wang
%%   Dust in Active Galactic Nuclei
%%   Aigen Li

The circumnuclear dust absorbs the AGN illumination and reradiates the absorbed energy in the IR. The IR emission at wavelengths longward of $\lambda > 1 \mu$m accounts for at least 50\% of the bolometric luminosity of type 2 AGNs. For type 1 AGNs, $\sim$10\% of the bolometric luminosity is emitted in the IR (e.g. see Fig. 13.7 of Osterbrock \& Ferland 2006). A near-IR ``bump'' (excess emission above the $\sim$2–10$\mu$m continuum), generally attributed to hot dust with temperatures around $\sim$1200– 1500K (near the sublimation temperatures of silicate and graphite grains), is seen in a few type 1 AGNs (Barvainis 1987; Rodriguez-Ardila \& Mazzalay 2006).

As discussed in detail in Stern et al. (2005, ApJ, 631, 163), the lack of strong polycyclic aromatic hydrocarbon emission in powerful AGNs, along with the IR flux $\lambda_{\rm rest} < 5 \mu$m flux of AGNs being dominated by power-law emission rather than a composite stellar spectrum, leads to the  AGNs being significantly redder than t
hat of lower-redshift galaxies. 

\smallskip
\smallskip
\noindent
Assef et al. (2013, ApJ, 772, 26; 2018, ApJS, 234, 23) have led the field in identiying large AGN candidate samples from selected from the Wide-field Infrared Survey Explorer (WISE) observations. 
From their most reliable study , Assef et al. (2018, ApJ, 866, 26) present spectroscopic observations of some of the most infrared variable extragalactic candidates to constrain their nature. {\it They find that from a sample of 45 objects with strong IR variablity, only seven show significant optical variability.}  

Investigations reveals that one of these objects, WISEA J094806.56+031801.7  is most likely a superluminous sue
pernova (SLSN) in W0948+0318 with total radiated energy to be $E=1.6\pm0.3 \times 10^{52}$ erg, {\it making it one of the most energetic SLSNe observed.} Based on the lack of change in mid-IR color throughout and after the transient event, we speculate that the location of the SLSN is within the torus of the AGN. 

\smallskip
\smallskip
\noindent
-- Ross et al., Stern et al. \\
-- but redder...\\

{\it With infrared emission from AGN associated with structures $\sim$a few light months to $\sim$several light years from the central engine accretion disk and photon source, variable AGN observed in the UV/optical during the early/mid 2020s from LSST will be NEOCam extragalactic time domain sources.}


\smallskip
\smallskip
\noindent
-- links to `ERQs' ?? \\
-- UFOs in the Seyferts (PDS456; Hamman et al.??) \\

\smallskip
\smallskip
\noindent
\textbf{\textsc{Connecting AGN activity in the IR with multi-messenger blazars: }}
With the electromagnetic association with GW1708017 (e.g., 
Abbott et al. 2017,  2017PhRvL.119p1101A	
Abbott et al. 2017,  2017ApJ...848L..12A	
Abbott et al. 2017,  2017ApJ...848L..13A	
Cowperthwaite et al. 2017,  2017ApJ...848L..17C	
Soares-Santos, et al. 2017,  2017ApJ...848L..16S)	

and the neutrino emission from the direction of the blazar TXS 0506+056

The era of ``multi-messenger astronomy'' 

The 3rd Generation Ground-based Gravitational-wave Observatory Network
(``3G'') and the ESA-NASA Laser Interferometer Space Antenna (LISA). 

Neutrino emission from the direction of the blazar TXS 0506+056
(IceCube Collaboration; 
2018, Science, 361, 146; 
2018, Science, 361, 147).


\smallskip
\smallskip
\noindent
-- Full LIGO mode
-- LISA

\smallskip
\smallskip
\noindent
%{\bfseries \large \textsc{\textcolor{Cerulean}{Continuing the NASA IR Space Telescope Legacy}}}
{\bfseries \textsc{\textcolor{Cerulean}{Time Domain Extragalactic Science in the 2030s}}}



\smallskip
\smallskip
\noindent
-- ``ROI'' in e.g. Exgal science for just the further data analysis. 

\smallskip
\smallskip
\noindent
NEOCam:: 65 -  120 $\mu$Jy for NC1 and 110-280 $\mu$Jy for NC2, 
WISE:: 0.08, 0.11 for W1/2 mJy, i.e. 80 and 110 $\mu$Jy.

\smallskip
\smallskip
\noindent
Overlapp with JWST??!!


\smallskip
\smallskip
\noindent
%\input{KeyNumbers_table}


\pagebreak
\textbf{References}



\end{document}

