%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%%  https://tex.stackexchange.com/questions/337820/mcq-long-table-using-tikz-tcolorbox-or-tabular
%%  https://tex.stackexchange.com/questions/283419/color-in-a-multirow-cell-with-extra-vertical-space/283454
%%  https://tex.stackexchange.com/questions/406033/how-to-fit-a-cell-of-a-table-to-a-figure-and-arrange-multiple-tables/406042
%% 
%% THIS (??)::
%%     https://texblog.org/2014/05/19/coloring-multi-row-tables-in-latex/
%%
%%
%%   https://www.inf.ethz.ch/personal/markusp/teaching/guides/guide-tables.pdf
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{tcolorbox}[tab1, tabularx={X  X }, title=Outstanding Issues in Infrared Time Domain Extragalactic Astrophysics, boxrule=1.25pt] 
Scientific Motivation                 &  NEOCam Requirements      \\ 
\hline \hline
\multicolumn{2}{c}{{\sc AGN IR Variablity and The Physics of Accretion}} \\ 
\hline
How many of the $\gtrsim$10 million IR identified AGN show (dramatic) IR variability?    &  Detection of large samples of IR AGN. Observe flux change of a factor of $\gtrsim2\times$ across 2-10$\mu$m \\
\hline
Investigate ``hot'' and ``cold'' (cf. the virial temperature) mode accretion in the 
AGN/quasar population; determine the rates and timescales characterising the 
Changing Look Quasar (CLQ) population.                                                                          &   Identify and characterize all the CLQs in DESI, LSST, WISE and NEOCam footprint.\\
\hline
%Probe and determine the physical state of the inner parsec of the quasar central engine.  & Rapid analysis and response for NEOCam quasar light curves. \\
%\hline
%%
\multicolumn{2}{c}{{\sc Obscured Accretion and Galaxy Formation}} \\
\hline
%%
Establish the bolometric output and origin of IR emission, and
determine presence of extreme outflows in the quasar population (??!!)                         &      Deep optical imaging data from LSST combined with searching for post-starburst signatures in NEOCam light-curves. \\
\hline
%%
Establishing the range of SED parameter space the quasars occupy by a 
multi-wavelength multi-epoch ``truth table dataset''.                                                  &      Build ``The Quasar SED Rosetta Stone'' using X-ray, UV/optical, IR data as well as repeat optical observations from LSST, NEOCam, spectroscopy. \\ 
\hline
\multicolumn{2}{c}{{\sc Cosmic Dawn}}\\
\hline
How many supermassive black holes are there after the first $\sim$800 
million years of the Universe?                                                                                         &      unWISE detects 80\% of the spectroscopically confirmed $z\geq6.70$ quasar population, and {\it all} of the known $z\geq7$ quasars (at 3-5$\mu$m) \\
%%
\multicolumn{2}{c}{{\sc Multi-messanger Astrophysics}}\\
\hline
Identify the EM counterparts for $\sim10^{6}$ M$_{\odot}$ supermassive 
binary black holes; Identify the EM counterparts for neutrino events.                            &  
\\ 
    %\end{tcbitemize}
\end{tcolorbox}
